\textbf{Beyond the Iceberg Hypothesis: \\Opening the Black Box of Transport Costs}\\Online Appendix (Not for publication)

### 2017-07-27 redaction/online_appendix_dhp2017.tex
modifsJH250717
Début révision texte et OA.
modifsJH270717
dernières modifs paper.

\urlstyle{rm}
\author{Guillaume Daudin\footnote{\noindent Corresponding author. Universit\'{e} Paris-Dauphine, PSL Research University, LEDa-DIAL, UMR 225, France \&
SciencesPo, Observatoire Français des Conjonctures \'{E}conomiques (OFCE), France; email: \url{guillaume.daudin@dauphine.fr}} \qquad \quad Jérôme Héricourt\footnote{\noindent Corresponding author. Université de Lille - LEM-CNRS (UMR 9221) and CEPII; email: \url{jerome.hericourt@univ-lille1.fr}} \qquad \quad Lise Patureau\footnote{\noindent Universit\'{e} Paris-Dauphine, PSL Research University, LEDa, France ; email: \url{lise.patureau@dauphine.fr}}}
%\date{\vspace{-5ex}}
%
%%\author[lille,brest,cepii]{J\'{e}r\^{o}me H\'{e}ricourt\fnref{fn1}}
%\fntext[fn1]{Corresponding author. Address: D\'{e}partement de Droit, \'{E}conomie, Gestion et AES, 12, Rue de Kergoat - CS 93837, 29238 Brest Cedex 3, France. Tel: (0033) 1 53 68 55 14. E-mail: jerome.hericourt@univ-brest.fr}
%\address[lille]{Univ. Lille, CNRS, IESEG School of Management, Institut Catholique de Lille, UMR 9221 - LEM - Lille Économie Management}
%\address[brest]{University of Brest-ICI (EA 2652), France}
%\address[cepii]{CEPII, France}
%
%\author[lille]{Clément Nedoncelle\fnref{fn2}}
%%\address[lille]{University of Lille - LEM-CNRS (UMR 9221), France}
%\fntext[fn2]{Address: Université de Lille, Facult\'{e} de Sciences \'{E}conomiques et Sociales, Cit\'{e} Scientifique - B\^{a}t SH2, 59655 Villeneuve d'Ascq Cedex, France. E-mail: clement.nedoncelle@ed.univ-lille1.fr}
%

@@

%
%XXXXXX
%
%
%			SECTION 2 / ALTERNATIVE MEASURES OF FIRM PERFORMANCE
%			
%			
%					
%XXXXXX
%
%
%
%

>>>>

\urlstyle{rm}
\author{Guillaume Daudin\footnote{\noindent Corresponding author. Universit\'{e} Paris-Dauphine, PSL Research University, LEDa-DIAL, UMR 225, France \&
SciencesPo, Observatoire Français des Conjonctures \'{E}conomiques (OFCE), France; email: \url{guillaume.daudin@dauphine.fr}} \qquad \quad Jérôme Héricourt\footnote{\noindent Corresponding author. Université de Lille - LEM-CNRS (UMR 9221) and CEPII; email: \url{jerome.hericourt@univ-lille1.fr}} \qquad \quad Lise Patureau\footnote{\noindent Universit\'{e} Paris-Dauphine, PSL Research University, LEDa, France ; email: \url{lise.patureau@dauphine.fr}}}
%\date{\vspace{-5ex}}

%Modèle additif seul
%+ableaux avec toutes les années en 3 digit et en 4 digit. Harmoniser la présentation des résultats (cf table 1 du papier)
%es résultats sur la version Hummels mais avec sa pondération: en annexe du papier? En online appendix?

@@

%
%XXXXXX
%
%
%			SECTION 2 / ALTERNATIVE MEASURES OF FIRM PERFORMANCE
%			
%			
%					
%XXXXXX
%
%
%
%\subsection{At a more disaggregated level}

\textbf{A mon avis, a mettre en online appendix. Expliquer comment se fait la decomposition en secteurs primaire/manuf.}

In this Section, we characterize the time trend in international transport costs at a more disaggregated level, by distinguishing the trade flows for primary goods and manufactured goods. The evolution in transport costs over time, by transport mode (overall transport costs and composition effects excluded) are reported in \ref{fig:totalTC_compeffects_excl_manuf} for the manufacturing sector, and in Figure \ref{fig:totalTC_compeffects_excl_primary} for the primary goods.

\begin{figure}[htbp]
\caption{Transport costs (with and without composition effects), Manufacturing}
\label{fig:totalTC_compeffects_excl_manuf}
\begin{center}
\includegraphics[height=4in]
{graph_composition_manuf.pdf}
\end{center}
\end{figure}

\begin{figure}[htbp]
\caption{Transport costs (with and without composition effects), Primary goods}
\label{fig:totalTC_compeffects_excl_primary}
\begin{center}
\includegraphics[height=4in]
{graph_composition_primary.pdf}
\end{center}
\end{figure}

\begin{figure}[htbp]
\caption{Share of primary goods in the value of total US imports}
\label{fig:Share_prim_goods}
\begin{center}
\includegraphics[height=4in]
{Share_of_primary.pdf}
\end{center}
\end{figure}

\textbf{A commenter. A mettre en Online Appendix?}
